Hydra Battles and Cie

### 2020-12-04 doc/chapter-powers.tex
Added traces of addition chains Small modification of the documentation

\section{Comparing Exponentiation Algorithms with respect to Efficiency}

@@

\subsection{Addition chains}
An \emph{addition chain} (In short : \emph{a chain})~\cite{brauer1939} is a representation of a sequence of
intermediate steps that lead to the evaluation of some $x^n$, under the 
assumption that each of these steps is a computation of  a power $x^i$, with 
$i<n$.

@@

From Module~\href{../theories/html/hydras.additions.Chains.html}{additions.Chains}

@@

@@

\section{Proving a chain's correctness}
\label{chain-correctness-sect}
In this section, we present various ways of proving that a given chain is 
correct w.r.t. a given exponent. First, we just try to apply 
the definition in Section~\vref{chain-correct-def}, but this method is very 
inefficient, even for small exponents. In a second step, we use more sophisticated techniques such as reflection and parametricity. Automatic generation of correct chains will be treated in Sect.~\vref{chain-generation}.

@@

\subsection{reflection tactic}
The tactic \texttt{monoid\_eq\_A} converts a goal of the form 
(\texttt{E\_eq $X$ $Y$}), where
\texttt{$X$} and \texttt{$Y$} are terms of type $A$, into
(\texttt{E\_eq (eval M  (model X)) (eval M  (model Y))}). This last goal is intended to be solved thanks 
to the lemma \texttt{flatten\_valid\_2}.

>>>>

\section{Comparing Exponentiation Algorithms with Respect to Efficiency}

@@

\section{Addition chains}
An \emph{addition chain} (In short : \emph{a chain})~\cite{brauer1939, additionchainspage} is a representation of a sequence of
intermediate steps that lead to the evaluation of some $x^n$, under the 
assumption that each of these steps is a computation of  a power $x^i$, with 
$i<n$.

@@

From Module~\href{../theories/html/hydras.additions.Addition_Chains.html}{additions.Addition\_Chains}

@@

\index{Projects}
\begin{project}
Define a function which returns the sequence of operations defined by a chain.
For instance, the chain \texttt{C87} of Figure \ref{fig:C87} can be represented as a 
list containing terms of the form \texttt{($i$, Add $j$ $k$)} whenever the associated computation contains the operation $x^i=x^j\times x^k$.

\begin{Coqsrc}
Compute chain_trace C87.
\end{Coqsrc}

\begin{Coqanswer}
(1, Init)
       :: (2, Add 1 1)
          :: (3, Add 2 1)
             :: (6, Add 3 3)
                :: (7, Add 6 1)
                   :: (10, Add 7 3)
                      :: (20, Add 10 10)
                         :: (40, Add 20 20)
                            :: (80, Add 40 40) :: (87, Add 80 7) :: nil
     : list (positive * info)
\end{Coqanswer}

\textbf{Note} A first solution (in ~\href{../theories/html/hydras.additions.Trace_exercise.html}{additions.Trace\_exercise}) consists in the definition of 
a (non-associative) multiplication over a type of trace, and apply the function
\texttt{chain\_execute} as if it were computing a power of \texttt{(1,Init)}.

@@

\section{Proving a Chain's Correctness}
\label{chain-correctness-sect}
In this section, we present various ways of proving that a given chain is 
correct w.r.t. a given exponent. First, we just try to apply 
the definition in Section~\vref{chain-correct-def}, but this method is very 
inefficient, even for small exponents. In a second step, we use more sophisticated techniques such as reflection and parametricity. Automatic generation of correct chains will be treated in Sect.~\vref{chain-generation}.

@@

\subsection{Reflection tactic}
The tactic \texttt{monoid\_eq\_A} converts a goal of the form 
(\texttt{E\_eq $X$ $Y$}), where
\texttt{$X$} and \texttt{$Y$} are terms of type $A$, into
(\texttt{E\_eq (eval M  (model X)) (eval M  (model Y))}). This last goal is intended to be solved thanks 
to the lemma \texttt{flatten\_valid\_2}.
